04-1 - Refitted models

### 2023-01-26 scripts/r/04-1_refitted.Rmd
♻️ - add note about manual up/download to/from OFS

Here's the code that does that for you.

```{r upload-refitted, eval=FALSE}
cache <- osf_retrieve_node("wds2m")
refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
  filter(name == "refitted")
models <- list.files(
  "./data/analyses/models",
  full.names = TRUE
)

osf_upload(
  refitted,
  path = models,
  recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
)
```

@@

```{r download-refitted, eval=FALSE}
cache <- osf_retrieve_node("wds2m")
refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)

osf_download(
  refitted_rds,
  path = "./data/analyses/models/",
  conflicts = "skip", progress = TRUE, verbose = TRUE
)
```

>>>>

~~Here's the code that does that for you.~~ The code has repeatedly failed to upload ALL models. Please upload manually.

```{r upload-refitted, eval=FALSE}
# cache <- osf_retrieve_node("wds2m")
# refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
#   filter(name == "refitted")
# models <- list.files(
#   "./data/analyses/models",
#   full.names = TRUE
# )
# 
# osf_upload(
#   refitted,
#   path = models,
#   recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
# )
```

@@

The code has repeatedly failed to download ALL models. Please download manually.

```{r download-refitted, eval=FALSE}
# cache <- osf_retrieve_node("wds2m")
# refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)
# 
# osf_download(
#   refitted_rds,
#   path = "./data/analyses/models/",
#   conflicts = "skip", progress = TRUE, verbose = TRUE
# )
```
